Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
editing...

We will leverage the following key observation: in order to maintain
the ``lucky'' property, it suffices to have $\NG$ $l$-th level groups
that observe disjoint sub-histories that take place in level
$(l - 1)$. Moreover, as long as the group size in levels lower than
$(l-1)$ are substantially smaller than group size of level $l-1$, the
``lucky'' property does not break even if different groups in level
$l$ observe overlapping sub-history from levels $\{1, \ldots, l-2\}$.

>>>>

We will leverage the following key observation: in order to maintain
the ``lucky'' property, it suffices to have $\Theta(\log T)$ $l$-th
level groups that observe disjoint sub-histories that take place in
level $(l - 1)$. Moreover, as long as the group size in levels lower
than $(l-1)$ are substantially smaller than group size of level $l-1$,
the ``lucky'' property does not break even if different groups in
level $l$ observe overlapping sub-history from levels
$\{1, \ldots, l-2\}$.
